Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-10-27 Cost_manuscript.Rmd
last 2 pars

  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands. Leveraging the ecological and computational richness of foraging paradigms will provide new insights on a number of open questions. First, the existence of a well-defined optimal choice strategy in foraging paradigms is useful for identifying when demands boost the value of rewards (i.e. overharvesting poor offers). Second, increasing the level of exposure to types of demands over two experiments will let us probe whether their cost is intrinsic or relative. Third, confronting participants with both mental and physical effort will let us probe whether these preferences are domain general or task-specific. Finally, modeling will help us disambiguate what drives these preferences. We predict that..

>>>>

  In this study, we tested the hypothesis that preferences would vary depending on whether individuals face a single or multiple types of behavioral demands (i.e. cognitive effort, physical effort, and delay). We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions. First, the existence of a well-defined optimal choice strategy in foraging designs was useful for identifying when demands boost the value of rewards (i.e. overharvesting poor offers). Second, increasing the level of exposure to types of demands over two experiments let us probe whether their cost is intrinsic or relative. Third, confronting participants with both mental and physical effort let us probe whether these preferences are domain general or task-specific. Finally, modeling helped us disambiguate what drove these preferences.

  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of whether they faced a single or intermixed demands. When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups underaccepted, partially matching our predictions and suggesting that cognitive effort can add value to outcomes. However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards. Computational modeling suggested that cognitive effort was valuable because it shortened the perceived time of trials, a phenomenon that could be recalibrated as individuals experienced multiple forms of demands (a detailed description of our preregistered hypotheses can be found on https://osf.io/2rsgm/). Our results expand our understanding of the attractiveness of effort, highlighting a role for features in the decision environment that are independent from a pure association between effort and reward.
